Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-06-25 kappa.tex
Develop SIA derivation.

\begin{equation}
    \left\{\begin{aligned}
        \pdv{\tau_{xz}}{z} &= \pdv{p}{x} \\
        \pdv{\tau_{yz}}{z} &= \pdv{p}{y} \\
        0 &= \pdv{p}{z} - \rho g
    \end{aligned}\right..
\end{equation}

@@

\begin{equation}
    \left\{\begin{aligned}
        \pdv{\tau_{xx}}{x} + \pdv{\tau_{xy}}{y} + \pdv{\tau_{xz}}{z}
            &= \pdv{p}{x} \\
        \pdv{\tau_{yx}}{x} + \pdv{\tau_{yy}}{y} + \pdv{\tau_{yz}}{z}
            &= \pdv{p}{y} \\
        \pdv{\tau_{zz}}{z} &= \pdv{p}{z} - \rho g
    \end{aligned}\right.,
\end{equation}

>>>>

\begin{equation}
    \label{eqn:sia}
    \left\{\begin{aligned}
        \pdv{\tau_{xz}}{z} &= \pdv{p}{x} \\
        \pdv{\tau_{yz}}{z} &= \pdv{p}{y} \\
        0 &= \pdv{p}{z} - \rho g
    \end{aligned}\right..
\end{equation}

The $z$-component of \cref{eqn:sia} gives the pressure (neglecting atmospheric
pressure),

\begin{equation}
    p = \rho g (s-z),
\end{equation}

which can be re-introduced into the $x$ and $y$-components, thus yielding the
expression of the horizontal shear stresses,

\begin{equation}
    \left\{\begin{aligned}
        \tau_{xz} &= \rho g (s-z) \pdv{s}{x} \\
        \tau_{yz} &= \rho g (s-z) \pdv{s}{x} \\
    \end{aligned}\right.,
\end{equation}

which are sometimes referred to as driving stresses. Using the constitutive
law (\ref{eqn:glenslaw}), vertical derivatives of horizontal velocities can
be related to the horizontal shear stresses,

\begin{equation}
    \left\{\begin{aligned}
        \pdv{v_x}{z} &= 2A (\tau_{xz}^2 + \tau_{yz}^2)^{n-1} \tau_{xz}\\
        \pdv{v_y}{z} &= 2A (\tau_{xz}^2 + \tau_{yz}^2)^{n-1} \tau_{yz}\\
    \end{aligned}\right..
\end{equation}

Thus, within the framework of the SIA, horizontal velocities $\vv_{SIA}$ can be
directly expressed as a function of the slope gradient,

\begin{equation}
    \left\{\begin{aligned}
        \pdv{v_x}{z} &= 2A (\rho g)^n (s-z)^n
                           (\pdv{s}{x}+\pdv{s}{y})^{n-1} \pdv{s}{x} \\
        \pdv{v_y}{z} &= 2A (\rho g)^n (s-z)^n
                           (\pdv{s}{x}+\pdv{s}{y})^{n-1} \pdv{s}{y} \\
    \end{aligned}\right.,
\end{equation}

or, in vectorial notation,

@@

\begin{equation}
    \label{eqn:ssa}
    \left\{\begin{aligned}
        \pdv{\tau_{xx}}{x} + \pdv{\tau_{xy}}{y} + \pdv{\tau_{xz}}{z}
            &= \pdv{p}{x} \\
        \pdv{\tau_{yx}}{x} + \pdv{\tau_{yy}}{y} + \pdv{\tau_{yz}}{z}
            &= \pdv{p}{y} \\
        \pdv{\tau_{zz}}{z} &= \pdv{p}{z} - \rho g
    \end{aligned}\right.,
\end{equation}
